Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-01-15 Journal1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (2)/pr.tex
first commit for new git

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
The purpose of this study is to optimize baseband resource allocation i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN system.
The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presents of the three generic service types introduced in 5G using RAN slicing.
In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and  user throughput.
We consider the limited fronthaul capacity and obtain the power and the capacity of each O-RU. We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We also model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\end{itemize}

\begin{figure*}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.6]{finalDraw.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}

@@

\subsection{Sub-Problem 1}\label{sub1}
Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
Here, we first simplify and relax the parameters to convexify the problem.

As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
for $\rho_{u(s,i)}^{k}$. 
Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{equation}
\begin{split}
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}\\
\end{split}
\end{equation}
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have 
$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$  
%\begin{equation}
%\begin{split}
%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
%\end{split}
%\end{equation}
In the following, we define a lemma to find the upper and lower bound for the optimal number of VNFs based on the achievable rates. Afterward, we obtain the formula to attain the optimal number of VNFs.  
\begin{lemma}
The optimal number of VNFs in each slice s can be achieved by the 
$M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s$.
where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.

\end{lemma}
%{\color{red} add one sentence before lemma to motivate why you need this lemma. The whole part is a lemma? It is too long. Where is the proof?}
\begin{proof}
In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as
$ \forall i,\forall s$
\begin{equation}
\begin{split}
&T^{\max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
\end{split}
\end{equation}
Also from equations in \eqref{c19}, \eqref{c16-1} and \eqref{c16-3}, we have
\begin{equation}
\alpha_s/\mu_s\leq M_s \leq \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}
\end{equation}
We denote $ \mathfrak{M}_s= \min\{M^{max}, \phi_{max}/{3\phi_s}\}$.
Thus, if we restrict constraint \eqref{c16} to equality, constraint \eqref{c16} is still valid.
Also, we have the following inequality.
\begin{equation}\label{eqDelay}
\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
\end{equation}
In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
the numerator and the denominator will both have the same sign.
In the numerator, according to the \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$, the numerator will be positive.
$(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$ since the order of $T^{max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{max}_s$.
Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{max}_s$.
So the numerator will be positive.
In the denominator, we can say that $(T^{max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,  
$\mu_s \geq 0$ and
$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{max}_s$ as mentioned above.
%Therefore, we need to have the constraint below.
%\begin{equation}\label{constraint16}
%\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
%\end{equation}

The left side of the equation \eqref{eqDelay}, leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ as below,
%\begin{equation}\label{RM}
%\begin{split}
%\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
% \mathit{\langle}_{u(s,i)}&=(T^{max}_s\mu_s-3)\lambda_{u(s,i)} + \mu_s,\\
%\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
%\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
%\end{split}
%\end{equation}
\begin{subequations}\label{RM}
\begin{alignat}{4}
\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\\
& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}\\
\end{alignat}
\end{subequations}
In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
$\mathtt{M}_{u(s,i)}$ in each slice as $M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s $.
%\begin{equation}
%M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
%\end{equation}
\end{proof}

Despite simplifying the problem in \eqref{problem}, it is still non-convex and hard to solve.
Therefore, the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.

>>>>

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
The purpose of this study is to optimize baseband resource allocation i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN system.
The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presents of the three generic service types introduced in 5G using RAN slicing.
In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and  user throughput.
We consider the limited fronthaul capacity and obtain the power and the capacity of each O-RU. We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We also model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\end{itemize}  
\begin{figure*}
    \includegraphics[scale = 0.6]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}

@@

\subsection{Sub-Problem 1}\label{sub1}
Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
Here, we first simplify and relax the parameters to convexify the problem.
As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
for $\rho_{u(s,i)}^{k}$. 
Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have 
$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$  
%\begin{split}
%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
%\end{split}
In the following, we define a lemma to find the upper and lower bound for the optimal number of VNFs based on the achievable rates. Afterward, we obtain the formula to attain the optimal number of VNFs.  
The optimal number of VNFs in each slice s can be achieved by the 
$M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s$.
where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
%{\color{red} add one sentence before lemma to motivate why you need this lemma. The whole part is a lemma? It is too long. Where is the proof?}
In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as
$ \forall i,\forall s$
&T^{\max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
Also from equations in \eqref{c19}, \eqref{c16-1} and \eqref{c16-3}, we have
\alpha_s/\mu_s\leq M_s \leq \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}
We denote $ \mathfrak{M}_s= \min\{M^{max}, \phi_{max}/{3\phi_s}\}$.
Thus, if we restrict constraint \eqref{c16} to equality, constraint \eqref{c16} is still valid.
Also, we have the following inequality.
\begin{equation}\label{eqDelay}
\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
the numerator and the denominator will both have the same sign.
In the numerator, according to the \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$, the numerator will be positive.
$(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$ since the order of $T^{max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{max}_s$.
Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{max}_s$.
So the numerator will be positive.
In the denominator, we can say that $(T^{max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,  
$\mu_s \geq 0$ and
$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{max}_s$ as mentioned above.
%Therefore, we need to have the constraint below.
%\begin{equation}\label{constraint16}
%\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
The left side of the equation \eqref{eqDelay}, leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ as below,
%\begin{equation}\label{RM}
%\begin{split}
%\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
% \mathit{\langle}_{u(s,i)}&=(T^{max}_s\mu_s-3)\lambda_{u(s,i)} + \mu_s,\\
%\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
%\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
%\end{split}
\begin{subequations}\label{RM}
\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\\
& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}
In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
$\mathtt{M}_{u(s,i)}$ in each slice as $M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s $.
%M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
Despite simplifying the problem in \eqref{problem}, it is still non-convex and hard to solve.
Therefore, the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.

In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint 
\eqref{c15} is changed to
 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
The combination of equations \eqref{c11} and \eqref{c15} leads to the following equation
\begin{equation} \label{pr11}
\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
P_r &\leq  \zeta_{r}.\\
Moreover, the combination of equations in \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
\begin{equation}\label{RConstr}
\eta_{u_{(s,i)}}&= \max\{\mathcal{R}_{u_{(s,i)}}^{\min}, \lambda_{u_{(s,i)}}+1/T^s_{\max}, \varpi_{u(s,i)} \}, \\
\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$, $\boldsymbol{\mathfrak{q}}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements. The Lagrangian function is written as 
\begin{subequations}\label{lagrang}
&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\delta_s\mathcal{\bar{R}}_{u_{(s,i)}}\\
&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\\
&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{max}_{s}- p^k_{r,u(s,i)})\\
&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\\
&-  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)} -1)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R} \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}.
